A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-17 manuscript/reply_to_reviewers.tex

		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the literature recommendations. We have incorporated these references as suggested (including Jordano, 2016 in the sampling section). Following comments from other reviewers, we have refined and restructured our introduction in the hope of more clearly establishing the goal of our manuscript. We hope that this revised introduction will also meet with the Reviewer's approval.

	3. Suggestion to de-emphasise MLE estimate and get straight to Bayes

		\begin{refquote}
		It's a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
		\end{refquote}

		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution that we use. Moreover, it helps to formalise our argument that most networks are undersampled, justifying the Bayesian approach and the use of priors to reduce/set bounds around the resulting uncertainty. We therefore feel that it is important to keep some discussion of the MLE estimate in the manuscript. We now introduce the MLE formally within this context (lines 178-184) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure S2, \emph{Appendix S2}).

### 2019-01-21 manuscript/reply_to_reviewers.tex

		\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta. We have therefore moved the description of basic properties to Appendix S3. The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.

	5. Novelty of the study not clear in current framing

		\begin{refquote}
		I'm wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE. Certainly, much of this logic is laid out in other works. The authors are well aware of this and have made significant contributions to this topic in the last few years. In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn't been covered. ...
		While it is true that none of the [suggested] papers do the exact same thing as this manuscript, they all	orbit the same topic. 
		\end{refquote}

		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion. We emphasise the broad applicability of our approach across network types and systems with varying degrees of prior knowledge. We also emphasise that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders). Finally, we note that there is a need to synthesise the literature on sampling issues and formalise the sources of uncertainty affecting the estimation of pairwise interactions. There are, as the Reviewer notes, already a number of publications addressing probabilistic interactions, but none of them adequately characterise uncertainty about interactions. We hope that the contribution our manuscript makes is now clearer.

@@

		Lines 354-357:

		\begin{quotation}
			the total number of co-occurrences was generally low (mean=3.87, median=2; Fig. 2A). The bulk (92.24\%) of these co-occurring species pairs were never observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, median=2; Fig. 2B) and was lower than the number of observed co-occurrences (Fig. 2C).
		\end{quotation}

	15. What does higher nestedness in the observed networks mean? How is it possible?

		\textbf{R:} Nestedness being higher in the observed networks simply means that the additional interactions predicted by our model tend not to be between generalists and specialists and, as such, do not contribute strongly to nestedness. This is actually somewhat intuitive - ``specialists'' in the observed data are exactly those species for which we are most likely to be missing interactions, and interactions between specialists are the most likely to be predicted to occur but not have been observed. Due to the tight word limit, we do not have space to discuss this extensively in the manuscript but have added brief interpretations in the results.

@@

		\textbf{R:} The redundant line has been removed. Thank you for pointing this out.

	10. Unsure about the point of filtering networks

		\begin{refquote}
		Line 295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
		\end{refquote}

		\textbf{R:} The filtering was intended to show how uncertainty likely warps our current understanding of network properties like connectance. If we do not observe 20-50\% of the interactions in a network, then many network properties in the published literature will be inaccurate. Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods versus only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees. Filtering networks in the way that we do could give an idea of how many interactions are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there). Due to length restrictions, we have moved this analysis to an appendix (\emph{Appendix S10}) and have rephrased these lines to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.

@@

		\begin{quotation}
			The probability of detecting an interaction also depends on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}. 
		\end{quotation}

	8. Confusion about goal of modelling

		\begin{refquote}
		I was struggling to really understand what the authors were really trying to model (partly because of the lack of a link between the theoretical and empirical parts of the paper). Are the authors trying to estimate L (the probability that an interaction is feasible or not – I would describe this as a `master' or meta- network), or is it that they are trying to estimate X|L (the probability that the interaction locally occurs)? I would be interested in both, but the second aspect seemed to be ignored in the gall-former example.
		\end{refquote}

		\textbf{R:} In the case study, we are modelling L (the probability that an interaction is feasible). We do not have quantitative data within sites in our dataset, so we cannot isolate the probability of detecting an interaction at a site from the probability that the interaction occurs. This is also the probability we were most interested in. We do note, however, that one could also model X|L using the same framework if there were independent counts of co-occurrences and interactions within a single site. \citet{Gravel2018} does just this. We now state throughout the manuscript that we are interested in compiling the metaweb, the set of interactions which can feasibly occur. We hope that our goal is now crystal clear.

### 2019-01-21 manuscript/CI_interactions.tex
Some minor fixes to the manuscript

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:

@@

  We obtained prior parameters of $\alpha_{ij}$=0.700, $\beta_{ij}$=8.49, giving a beta distribution strongly skewed towards 0. Where $n=0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda_{ij}$)=0.008. When $n=374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76$\times10^6$. This distributions is very close to 0 with small variance about $\lambda_{ij}$; if species $i$ and $j$ co-occurred 374 times without interacting, they are extremely unlikely to do so at other sites or times.

>>>>

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_{ij}$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:

@@

  We obtained prior parameters of $\alpha_{ij}$=0.700, $\beta_{ij}$=8.49, giving a beta distribution strongly skewed towards 0. Where $n=0$, these parameters gave a posterior distribution with $\bar\lambda_{ij}$=0.076, var($\lambda_{ij}$)=0.008. When $n=374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76$\times10^6$. This distribution is very close to 0 with small variance about $\lambda_{ij}$; if species $i$ and $j$ co-occurred 374 times without interacting, they are extremely unlikely to do so at other sites or times.
